---
title: 'Peer-graded Assignment: R Markdown Presentation & Plotly'
author: "jacethedatascientist"
date: "August 14, 2019"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

In this project, we will create a web page presentation using R Markdown that features a plot created with Plotly. We'll host our webpage on either GitHub Pages, RPubs, or NeoCities. 

Our webpage must contain the date that we created the document, and it must contain a plot created with Plotly. 

## Preparation

```{r , echo = TRUE, cache = TRUE, warning = FALSE, message = FALSE}
library(plotly)
library(dplyr)
library(Ecdat)
data(Icecream)
```

```{r , echo = TRUE, cache = TRUE}
head(Icecream)
```

## Data Format
<br>
**Summary**
The Ice cream dataset (*Icecream*) is a four-weekly observations from March 18, 1951 to July 7, 1953.

It's consists of 30 observations from the United States.

**Variables:**

* cons - Ice Cream consumption per head (in pints)
* income - Average family income per week (USD)
* price - Price of ice cream (per pint)
* temp - Average temperature (in Fahrenheit)
<br>
<br>
**Source:**
*Hildreth, C. and J. Lu (1960) Demand relations with autocorrelated disturbances, Technical Bulletin No 2765, Michigan State University.*

## Relationship Between the Local Temperature and The Ice Cream Consumption in the US
<br>
<center>
```{r , echo = FALSE, cache = TRUE}
reglin <- lm(cons ~ temp, data = Icecream)
ice_plot <- plot_ly(data = Icecream, x = ~temp, y = ~cons, type = 'scatter', mode = 'markers', name = "Plot") %>% layout(title="Consumptions Based on Humidity", xaxis=list(title="Temperature (Fahrenheit)"), yaxis=list(title="Consumption (pint)")) %>% add_trace(y = reglin$fitted.values, type = "scatter", mode = "lines", name = "Regression Line", line = list(width = 2))

ice_plot
```
</center>

Based on the graph above, the *temperature* in the locals' area is **_correlated_** to the amount of their *ice cream consumptions*.
