---
title: "Developing Data Products Assignment 1"
author: "jacethedatascientist"
date: "August 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### **Peer-graded Assignment : R Markdown and Leaflet**
###### *Jace Galleon*

***

#### I. Project Overview
In this project, we will create a web page using R Markdown that features a map created with Leaflet. 

After creating, we'll host our webpage on either GitHub Pages, RPubs, or NeoCities.

***

#### II. Project Objective
Our webpage must contain:
1. The date that you created the document; and
2. A map created with Leaflet.

Make it as creative as possible.

#### III. Project Execution
##### A. Library Loading
```{r , cache = TRUE, echo = TRUE}
library(leaflet)
```

***

##### B. Mapping
<center>
```{r , cache = TRUE, echo = TRUE}
my_map <- leaflet() %>% addTiles() 
my_map <- my_map %>% addMarkers(lng=121.0499036, lat=14.5534542, popup="The Globe Tower")
my_map
```
</center>
***

*This formally ends the Course Project. Thank You!*
