---
title: "Shiny Application and Reproducible Pitch"
author: "jacethedatascientist"
date: "August 15, 2019"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## <code>Introduction</code>

This is the Final Project of the Developing Data Products.

The App was created to compute the Body Mass Index for Male and Female in terms of English Metric and International Metric System of Units.

## <code>What is a Body Mass Index?</code>
**Body mass index (BMI)** is a value derived from the *mass (weight)* and *height* of a person. The BMI is defined as the *body mass divided by the square of the body height*, and is universally expressed in units of **kg/m^2^**, resulting from mass in *kilograms* and height in *metres* or in <code>lbs</code> and <code>in</code>.

Shiny App : https://jacethedatascientist.shinyapps.io/bmi_calculator/  
GH Repo : https://github.com/jacethedatascientist/DevelopingDataProducts

---
```{r, echo = FALSE}
library(shiny)
shinyAppDir(
  system.file("examples/BMI Calculator", package="shiny"),
  options = list(width = "100%", height = "100%")
)
```

## <code>How to Use the Body Mass Index Calculator?</code>
1. Select your preferred *Metric System* that you will use as the BMI computations for both metrics is **different**.
2. Select your *Gender* as the BMI classification is **different** among male and female.
3. Click Reset to **clear** the menus.


## <code>Body Mass Index Calculator</code>
<br>
That's it!
<br>
You may now go back to the application and input the necessary details to determine your BMI.
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
*This formally ends the Course Project. Thank You!*

